# Convert accession numbers to taxonomy

<!--
[![Build Status](https://travis-ci.org/sherrillmix/taxonomizr.svg?branch=master)](https://travis-ci.org/sherrillmix/taxonomizr)
[![codecov](https://codecov.io/gh/sherrillmix/taxonomizr/branch/master/graph/badge.svg)](https://codecov.io/gh/sherrillmix/taxonomizr)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/taxonomizr)](https://cran.r-project.org/package=taxonomizr)
-->

## Introduction

`antiprofr` provides some simple functions to read in and display measurements of antibody profiling in serum.

The major functions are:
 * `readAnti`: read in antibody profiling data
 * `convertStackedToMat`: average stacked data to a single value per patient-antigen
 * `plotAnti`: plot the raw data from positive controls and patient serum
 * `plotHeat`: plot the average patient-antigen values

And a simple use case might look like (see below for more details):

```{r,eval=FALSE}
library(antir)
raw<-read.csv('antibodyData.csv',stringsAsFactors=FALSE,header=FALSE)
stacked<-readAnti(raw,p24Cut=10)
odMat<-convertStackedToMat(stacked)
par(mar=c(6,10,1,3))
plotHeat(odMat,main='',filterLess=200,filterMore=50000,scaleMain='Dilution reaching OD450(p24=10pg)')
```

## Installation
The package is available from github, use the [<code>devtools</code>](https://github.com/hadley/devtools) library and run:
```{r, eval=FALSE}
devtools::install_github("sherrillmix/antir")
```

To use the library, load it in R:
```{r}
library(antir)
```

## Usage

### Data format

This package is designed for antibody profiling data where each row given the OD for various dilutions of a patient serum with a given antigen (or positive or negative control). The data should be in a 15 column .csv where the first column gives the patient ID (blanks are filled down), the second column gives the antigen and columns 3-14 give OD values for given dilutions of the patient serum for that antigen.

### Reading in data
In most cases, the user will be reading in data from a .csv file (if an Excel file then Save As .csv in Excel or OpenOffice):

```{r,eval=FALSE}
raw<-read.csv('antibodyData.csv',stringsAsFactors=FALSE,header=FALSE)
```

Here we'll use data cached from the package:

```{r}
raw<-antibodyData
head(raw)
```


